Objective-First Nanophotonic Design Plan

### 2012-11-27 plan/plan.tex
Get computation of delta x_i.

\subsubsection{Computation of $\Delta x_i$}
We now show how $\Delta x_i$ may be efficiently computed.

>>>>

\subsubsection{Computation of $\Delta x_i$}
We now show how $\Delta x_i$ may be efficiently computed.
First we introduce
    \E{}{\tilde{c}_i = \frac{1}{\rho t} \sum_j r_j A^{-\cT} c_{ij}}
    in order to write
    \E{}{\grad_{x_i} \Lag(x, z, u) = \rho A_i(z)\T(A_i(z)x_i - b_i(z) 
                            + u_i + \tilde{c}_i).}
For its part, the Hessian can be simplified using the matrix inversion lemma\footnote{\E{}{ (A + UCV)^{-1} = A^{-1} - A^{-1}U (C^{-1} + V A^{-1} U)^{-1} V A^{-1}}}.
Coupled with the introduction of 
    \E{}{\tilde{C}_i = A_i(z)^{-\cT}\begin{bmatrix} 
                        \sqrt{\frac{s_1}{\rho t}}c_{i1} &
                        \sqrt{\frac{s_2}{\rho t}}c_{i1} &
                        \cdots &
                        \sqrt{\frac{s_{m_i}}{\rho t}}c_{im_i} 
                        \end{bmatrix}}
    we can write
    \E{}{\grad_{x_i}^2 \Lag(x, z, u) = \rho A_i(z)\T (I + \tilde{C}\tilde{C}\T) A_i(z),}
    and more importantly
    \E{}{(\grad_{x_i}^2 \Lag(x, z, u))^{-1} = \frac{1}{\rho} A_i(z)^{-1} M A_i(z)^{-\cT},}
    where
    \E{}{M = (I + \tilde{C} \tilde{C}\T)^{-1} = 
            I - \tilde{C} (I + \tilde{C}\T\tilde{C})^{-1} \tilde{C}\T.}

Finally, the expression for $\Delta x_i$ is obtained as
    \E{}{\Delta x_i = - \grad^2_{x_i} \Lag^{-1} \grad_{x_i} \Lag = 
        A_i(z)^{-1} M (A_i(z)x_i - b_i(z) + u_i + \tilde{c}_i).}
